PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-06-25 manuscript_00.Rmd
swap in covariate for plot

o_ct <- meta_filter %>% filter(Tissue == 'Retina') %>% pull(CellType)
p_data <- meta_filter %>% 
  #mutate(CellType_predict = Tissue) %>% 
  #mutate(CellType_predict = case_when(!CellType_predict %in% ws_oct ~ 'Other',
  #                                    TRUE ~ CellType_predict)) %>% 
  filter(Organ == 'Eye') %>% 
  mutate(Citation = paste(str_trunc(Citation, width = 20), str_trunc(batch, side = "left", width = 15))) %>% 
  group_by(Citation, organism, Tissue, CellType_predict) %>% 
  summarise(Count = n()) %>% 
  mutate(Proportion = Count/sum(Count) * 100)

>>>>

o_ct <- meta_filter %>% filter(Tissue == 'Retina') %>% pull(CellType)
p_data <- meta_filter %>% 
  #mutate(CellType_predict = Tissue) %>% 
  #mutate(CellType_predict = case_when(!CellType_predict %in% ws_oct ~ 'Other',
  #                                    TRUE ~ CellType_predict)) %>% 
  filter(Organ == 'Eye') %>% 
  mutate(Citation = paste(str_trunc(Citation, width = 20), Covariate)) %>% 
  group_by(Citation, organism, Tissue, CellType_predict) %>% 
  summarise(Count = n()) %>% 
  mutate(Proportion = Count/sum(Count) * 100)
